---
title: "IMDB Movie Analysis"
author: "Tran Le"
output:
  html_document:
    df_print: paged
  html_notebook: default
---

```{r setup, include=FALSE}


library(knitr)

# As long as you are working in a Rstudio Project file, you shouldn't need to 'hard code' directories like this 
# change to your own working directory
#knitr::opts_knit$set(root.dir = 'C:/Users/doosti/Desktop/MGSC_310')

# set seed to your own favorite number
set.seed(310)
options(width=70)
# if you want to prevent scientific format for numbers use this:
options(scipen=99)

# general rchunk code options
opts_chunk$set(tidy.opts=list(width.wrap=50),tidy=FALSE, size = "vsmall")
opts_chunk$set(message = FALSE,
               warning = FALSE,
               cache = TRUE,
               autodep = TRUE,
               cache.comments = FALSE,
               collapse = TRUE,
               fig.width = 5,  
               fig.height = 4,
               fig.align='center')

```

```{r setup_2}

# load all your libraries here
library('tidyverse')

```


### IMDB-5000 Dataset
```{r}

movies <- read.csv("datasets/IMDB_movies.csv")

movies %>% glimpse()

```


### Order the dataset in descending order by gross or total box office revenue in $USD. Show the ten movies with the largest box office revenue in the dataset. Which director is the king of the box office?

```{r}

movies %>% 
  arrange(-gross) %>% 
  slice(1:10) 

```
The king of the box office is James Cameron.
<br />
<br />

### Remove the variable `facenumber_in_poster`. Store the smaller dataset as `movies_sub`. Run the dimension command to ensure that `movies_sub` has one fewer variable than movies.

```{r}

movies_sub <- 
  movies %>%
  select(-facenumber_in_poster)

dim(movies_sub)

```
<br />
<br />

### How many movies are rated as PG-13? What is the average revenue (gross) for PG-13 movies? 

```{r}

movies %>%
  filter(content_rating == "PG-13") %>%
  summarize(num_movies = n(),
            avg_revenue = mean(gross, na.rm = TRUE))

```
There are 1329 PG-13 movies. The average revenue for PG-13 movies is $68,270,240.	

<br />
<br />

### Create a new variable `gross_M` that lists gross in millions of dollars. Store this new variable in the movies dataset. 

```{r}

movies <- 
  movies %>% 
  mutate(gross_M = gross/1000000)

```
<br />
<br />

### Is there a relationship between movie gross and IMDB score?

```{r}

ggplot(movies, aes(imdb_score, gross_M)) +
  geom_point(alpha = 0.1) + 
  xlab("IMDB Score") +
  ylab("Movie Gross ($USD)") +
  labs(title = "IMDB Score vs Movie Gross") +
  geom_smooth(method="lm")

```
Given the line, there seems to be a slight positive relationship between IMDB Score and Movie Gross.
<br />
<br />

### Plot movie gross against IMDB score for James Cameron films, where the points are the movie titles. 

```{r}

ggplot(movies %>% filter(director_name == "James Cameron"),
       aes(imdb_score, gross_M)) +
  geom_text(aes(label = movie_title), color = "blue") + 
  xlab("IMDB Score") +
  ylab("Movie Gross ($USD)") +
  labs(title = "IMDB Score vs Movie Gross for James Cameron's Films") +
  geom_smooth(method="lm")+
  xlim(7.1, 8.9) +
  ylim(0, 800)

```
<br />
<br />
